Kaggle-in-class Data Challenges Can Boost Student Learning

### 2019-09-23 paper-kaggle.Rmd
think we are done with revision. need to make all responses the same blue colour

The number of submissions that a student made, may be an indicator of performance on the exam questions related to the competition.  A student who is more engaged in the competition may learn more about the material, and consequently perform better on the exam. Figure \ref{fig:numsubmition} (top row) shows performance on the classification and regression questions, respectively, against their frequency of prediction submissions for the three student groups (MAST90083 classification and regression, ETC5242 regression) competitions. The relationship is weak in all groups, and this mirrors insignificant results from a linear model fit to both subsets. On the other hand, the predictive accuracy improved with the number of submissions for the regression competitions. There appears to be some nonlinearity present in these plots, suggesting reduced returns, less reduction in error as more attempts are made. That is reasonable to expect. Also, some students strategically make very poor initial predictions to get a baseline on error corresponding to guessing.

>>>>

The number of submissions that a student made, may be an indicator of performance on the exam questions related to the competition.  A student who is more engaged in the competition may learn more about the material, and consequently perform better on the exam. Figure \ref{fig:numsubmition} (top row) shows performance on the classification and regression questions, respectively, against their frequency of prediction submissions for the three student groups (MAST90083 classification and regression, ETC5242 regression) competitions. The relationship is weak in all groups, and this mirrors insignificant results from a linear model fit to both subsets. On the other hand, the predictive accuracy improved with the number of submissions for the regression competitions. There appears to be some nonlinearity present in these plots, suggesting reduced returns. That is reasonable to expect. Also, some students strategically make very poor initial predictions, to get a baseline on error equivalent to guessing.
